COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging

### 2021-05-04 paper_files/figure-latex/genderhist-1.tex
drop drive calls
update
no google drive
paper
update files

% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:44
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,635.84) {If a COVID-19 vaccine becomes available in [country], would you take it?};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-05-04 13:13:07
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,635.84) {Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine?};
\end{scope}
\end{tikzpicture}
